Algomusicology, ????, Profit

### 2016-04-03 paper.tex
Fix some more references.

The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig\cite{Leipzig},
a music theory library,
\footnote{Leipzig provides ways of describing notes in terms of higher order concepts like chords and scales.}
and Midje\cite{Midje}, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
which asserts that expression evaluates to result.}

@@

Here is an example of using these definitions to calculate the description and result length of a short sequence of Gs.

@@

Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
is a better description of the piece than the raw notes.

@@

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest"?????. In other words, that one book
epitomises the complexity of the entire library.

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}.

@@

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})
\bibitem{Air on the G String} Bach, Johann Sebastian: Air on the G String
\bibitem{The Library of Babel} Borges, Jorge Luis
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
\bibitem{Leipzig} Ford, Chris: Leipzig
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
\bibitem{Midje} Marick, Brian: Midje
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
\bibitem{Contact} Sagan, Carl: Contact
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines

>>>>

The examples in this paper are all written in Clojure\cite{Clojure}, a dialect of Lisp. I also rely on Leipzig\cite{Leipzig},
a music theory library, and Midje\cite{Midje}, a unit testing library.

@@

Here is an example of using these definitions to calculate the description and result length of a short sequence of Gs.
The \verb|fact| notation is due to Midje, which allows us to write \verb|(fact expression => result)|,
which asserts that \verb|expression| evaluates to \verb|result|.

@@

Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
is a better description of the piece than the raw notes. The music functions e.g. \verb|phrase| are due to Leipzig,
and emit a time series data structure representing the resulting notes. \verb|;| indicates a comment in Clojure.

@@

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
epitomises the complexity of the entire library.

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}
\cite{USA Today}.

@@

Thank you also to Sam Aaron and Jeff Rose for giving the world Overtone\cite{Overtone}, the audio programming environment
that made this paper possible.

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String
\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
\bibitem{Leipzig} Ford, Chris: Leipzig
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
\bibitem{Clojure} Hickey, Rich: Clojure
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
\bibitem{Midje} Marick, Brian: Midje
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye (\url{http://www.usatoday.com/story/life/music/2015/03/10/blurred-lines-trial-verdict/24492431/})
\bibitem{Contact} Sagan, Carl: Contact
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines
